---
title: "ReadMe For the Team"
output:
  html_document:
    code_folding: show
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    theme: paper
    highlight: tango
editor_options: 
  chunk_output_type: console
---


This document is for team and explain steps to install or use libraries.<br>
Feel free to correct any mistake or add solutions for any encountered problems. <br>
Don't forget: with "history" command you can retrieve the old commands you've typed. <br>

# Recommandations for the Read Me Client
For the readme_client don't forget to put the version of the library or anything you use and if relevant add the commands/the steps/documentation to properly use them. 

For the commands, I recommand to put them on a chunk to conserve structure. To avoid execution of the chunk put "{r, eval = FALSE}" in the header of the chunk like so: 

```{r, eval = FALSE}
blabla
```


# Data Base 
For the database, table names as well as attributes names are available on the google docs
Note: the "type" attribute (associated with the COG table) has been replaced by "category" since it's a reserved keyword <br>
(see here: https://stackoverflow.com/questions/15150798/is-type-a-reserved-word-in-mysql) <br>
Same for "status" in the same table. 

To install mysql see the steps here: https://tecadmin.net/install-mysql-8-on-fedora/
Be careful there is a temporary password, you need to configure your own password after installation. <br> **DO NOT USE THE SAME PASSWORD FOR YOU COMPUTER (sudo command) AND MYSQL**
for security reason.


If you forgot the temporary password don't panic: here is how to retrieve it: 

```{r, eval = FALSE}
sudo grep 'temporary password' /var/log/mysqld.log
```

To execute mysql in the shell
```{r, eval = FALSE}
mysql -u root -p
```

# How to connect to your local database without changing password in the shared .py
The idea is to create a python file **that you won't share** (already in the .gitignore file) with variables containing our own password.
Once created you import this file in the shared python file (and so you import your password but hidden in the variable) and use those variables. To make it work you need to use the same name for the variables and the file's name as all the users (so us) !

Here the procedure step by step: 

You need to create a directory called "configurations" <br>
Then in this directory create a file called config.py <br>
Then open this file and complete the following code <br>
```{r, eval = FALSE}
BD_USER = "yourusername" #Probably root
BD_PASSWORD = "yourpassword" #mysql password (the one you configure)
```
Test if it works by executing the Data_Treatment.py file 


