---
title: "ReadMe For the Team"
output:
  html_document:
    code_folding: show
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    theme: paper
    highlight: tango
editor_options: 
  chunk_output_type: console
---


This document is for team and explain steps to install or use libraries.<br>
Feel free to correct any mistake or add solutions for any encountered problems. <br>
Don't forget: with "history" command you can retrieve the old commands you've typed. <br>

# Recommandations for the Read Me Client
For the readme_client don't forget to put the version of the library or anything you use and if relevant add the commands/the steps/documentation to properly use them. 

For the commands, I recommand to put them on a chunk to conserve structure. To avoid execution of the chunk put "{r, eval = FALSE}" in the header of the chunk like so: 

```{r, eval = FALSE}
blabla
```


# Data Base 
For the database, table names as well as attributes names are available on the google docs
Note: the "type" attribute (associated with the COG table) has been replaced by "category" since it's a reserved keyword <br>
(see here: https://stackoverflow.com/questions/15150798/is-type-a-reserved-word-in-mysql) <br>
Same for "status" in the same table. 

To install mysql see the steps here: https://tecadmin.net/install-mysql-8-on-fedora/
Be careful there is a temporary password, you need to configure your own password after installation. <br> **DO NOT USE THE SAME PASSWORD FOR YOU COMPUTER (sudo command) AND MYSQL**
for security reason.


If you forgot the temporary password don't panic: here is how to retrieve it: 

```{r, eval = FALSE}
sudo grep 'temporary password' /var/log/mysqld.log
```

To execute mysql in the shell
```{r, eval = FALSE}
mysql -u root -p
```

# How to connect to your local database without changing password in the shared .py
The idea is to create a python file **that you won't share** (already in the .gitignore file) with variables containing our own password.
Once created you import this file in the shared python file (and so you import your password but hidden in the variable) and use those variables. To make it work you need to use the same name for the variables and the file's name as all the users (so us) !

Here the procedure step by step: 

You need to create a directory called "configurations" <br>
Then in this directory create a file called config.py <br>
Then open this file and complete the following code <br>
```{r, eval = FALSE}
BD_USER = "yourusername" #Probably root
BD_PASSWORD = "yourpassword" #mysql password (the one you configured)
```
Test if it works by executing the Data_Treatment.py file 


# SSL Problem
https://stackoverflow.com/questions/27835619/urllib-and-ssl-certificate-verify-failed-error

To do requests on the database we need a SSL certificate.An SSL certificate is a type of digital certificate that provides authentication for a website and enables an encrypted connection. To provide this certificate here is the answer found on stack overflow (it's not the first one).

"I was having a similar problem, though I was using urllib.request.urlopen in Python 3.4, 3.5, and 3.6. (This is a portion of the Python 3 equivalent of urllib2, per the note at the head of Python 2's urllib2 documentation page.)

My solution was to pip install certifi to install certifi, which has:

... a carefully curated collection of Root Certificates for validating the trustworthiness of SSL certificates while verifying the identity of TLS hosts.

Then, in my code where I previously just had:

import urllib.request as urlrq

resp = urlrq.urlopen('https://example.com/bar/baz.html')
I revised it to:

import urllib.request as urlrq
import certifi

resp = urlrq.urlopen('https://example.com/bar/baz.html', cafile=certifi.where())
If I read the urllib2.urlopen documentation correctly, it also has a cafile argument. So, urllib2.urlopen([...], certifi.where()) might work for Python 2.7 as well.

UPDATE (2020-01-01): As of Python 3.6, the cafile argument to urlopen has been deprecated, with the context argument supposed to be specified instead. I found the following to work equally well on 3.5 through 3.8:
import urllib.request as urlrq
import certifi
import ssl

resp = urlrq.urlopen('https://example.com/bar/baz.html', context=ssl.create_default_context(cafile=certifi.where()))"

# New solution with requests library
First, you need to connect to mysql and drop all the tables in database ptut
since all the tables have been renamed and the drop argument will therefore not work.

Second, once in your conda environment you need to install the resquests library with this following commande: 

```{r eval = False}
pip install requests 
```

Third, you need to download the table from eggnog with the description and the type of each eggnog called 2157_annotations.tsv at this adress. **Don't fortget to put it in the "data" directory to not push it in the gitlab** 

http://eggnog5.embl.de/download/eggnog_5.0/per_tax_level/2157/

Finally, a new argument has been added in pipeline '-c' for the annotation file. To execute Pipeline.py use the following command (adapt if path different).
/!\ You may need to add execution right for Pipeline.py 

```{r eval = False}
./Pipeline_helicase.py -f data/sf2pfams_archA-sp.tsv -c data/2157_annotations.tsv 
```

